Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-05-02 tex/paper1/paper1.tex
edits to the model fitting appendix

Figures \ref{fig:dist171} and \ref{fig:dist193} show that the
logarithm of the Fourier power in a region of the Sun may be
approximated by a normal distribution $N(\mu, \sigma)$.  The maximum
likelihood estimate of the mean and variance of normal distribution
are given by
\begin{equation}
\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
\label{eqn:mlmean}
\end{equation}
where $N$ is the number of independent measurements.  The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}

>>>>

As noted in Section \ref{sec:anal}, the logarithm of the Fourier power for all
regions may be approximated by a normal distribution $N(\mu, \sigma)$.
The maximum likelihood estimate of the mean and variance of normal
distribution are given by
\begin{equation}
\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
\label{eqn:mlmean}
\end{equation}
and
\begin{equation}
\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
\label{eqn:mlmean}
\end{equation}
where $N_{pixel}$ is the number of pixels in each region.

The estimated
error in the estimated error is
\begin{equation}
\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
\label{eqn:mlmean}
\end{equation}
